%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------
\chapter{Introduction}
%------------------------------------------------

\section{What is this book?}
\begin{fullwidth}

2 sections, 57 chapters, loads of fun.
problems of shooting and problems of stitching.
solutions to those problems.
all the techniques to slay all your demons.
the book can be read in any random order or end to end cover to cover.
however you like.
the manual will be free. an open source version will be available for download in pdf format. there will also be a limited edition batch of hardcopy books for those who like to learn the analog way.

\end{fullwidth}

%------------------------------------------------

\section{Who is this book for?}
\begin{fullwidth}

artists, pioneers, adventurers, astronauts, cowboys and cowgirls; basically anyone who wants to start experimenting on this new medium can join us. we have paved a path and laid stepping stones across this great divide for you to cross the river and join us in exploring a new land! we are sharing every tip and trick we have painfully learned ourselves so you can skip right to having fun. we only ask that you remember to come back and share your findings with everyone so we can build a community!

\end{fullwidth}

%------------------------------------------------
\section{How to use this book?}
\begin{fullwidth}
\end{fullwidth}
%----------------------------------------------------------------------------------------

\section{How this book is organized?}
\begin{fullwidth}
\end{fullwidth}
%----------------------------------------------------------------------------------------

\section{Why is this book needed}
\begin{fullwidth}

we want to build a community by sharing everything we’ve learned about making professional 360 videos over the last 3 years. right now, there is very little documentation on the process, from start to finish, for creating narrative virtual reality films. by writing making360 our goal is to help those who are excited about exploring new storytelling techniques by aiding in skipping the initial hazing process. by sharing our experiences, we will be able to speed up your learning curve. creating 360 videos is very intense and detailed so we’re here to walk you through it!


\end{fullwidth}
%----------------------------------------------------------------------------------------
