\chapter{Dymaxion Chronofile}
\pagecolor{white}
\label{chap:27}
\begin{fullwidth}


{\itshape\bfseries “So, planners, architects, and engineers take the initiative. Go to work, and above all co-operate and don't hold back on one another or try to gain at the expense of another. Any success in such lopsidedness will be increasingly short-lived. These are the synergetic rules that evolution is employing and trying to make clear to us. They are not man-made laws. They are the infinitely accommodative laws of the intellectual integrity governing universe.”}

- Buckminster Fuller, Operating Manual For Spaceship Earth
\vspace{\baselineskip}

\problem

{\large You have devils of details to worry about. \par}

Be organized! Number your cards as well as cameras. Color code your cameras if you have \textbf{\nameref{chap:10}}. This will prevent headaches and confusion during \textbf{\nameref{chap:29}} and post production. There are all the normal problems of shooting times x amount of cameras so proceed with extra care. Remember to give yourself \textbf{\nameref{chap:22}} for \textbf{\nameref{chap:33}} during post. Prepare for the shoot by \textbf{\nameref{chap:04}}, resetting the \textbf{\nameref{chap:05}} on all your cameras, and charging extra batteries. 


\solution

{\large Get a journal or notebook to keep track of production notes, takes, the month and date of each new morning, and share your growth! \par}

We hear the phrase “new cinematic language” everyday. What does that look and sound like? A single person alone can’t write an entire language. Then there would be no dialogue. We need to all create grammar, vocabulary, words, sentences, poems and build the structure together. Share and compare your findings. New words arise from a common need.  Let’s write!




\clearpage
\end{fullwidth}
