\chapter{ Platonic Rigs}
\pagecolor{white}
\label{chap:1}
\begin{fullwidth}

\problem

{\large You need to choose a 360 camera rig from all the options and configurations available.
 \par}

6 camera? 7, 10? or 3 cameras with modified fisheye lens? mono or stereo? spherical or cylindrical? One size does not fit all. Don’t worry, we’ll find the perfect fit. Selecting a rig depends on the type of content you are shooting, environment, distance, moving shots and of course money in the piggy bank.

\solution

{\large Prioritize your needs.
 \par}

MONO vs STEREO
First decide between monoscopic or stereoscopic. This comes down to cost. Stereo will give depth to the subjects and objects, enhancing the quality of experience but the costs will be significantly greater in both hardware and post production. If you have the budget and manpower, then stereo for the win! The difference is astounding and makes the experience more vivid and real. 

If you are shooting on a tight budget look at the type of content you are shooting. Will the subjects and objects be close? If they are at farther distances or if you are shooting landscapes without close subjects, the stereo effect won’t be as noticeable. You should save your money for a different aspect of the production. Another factor to keep in mind is how much control you have over the environment. If you are shooting a live event like news or sports then it will be difficult to control variables like subjects moving between seams of the cameras. The parallax and flaws between cameras is even more apparent especially for differences between stereo pairs. The errors will exponentially compound and cause viewing discomfort, eyestrain, and nausea. Shooting on set where you can control variables and block movement will be best for stereo. If you are sending a stereo rig into the field, be prepared for potentially heavy post production since environment variables will be out of your control. 

With monoscopic videos you will be able to get higher resolution. To playback stereoscopic videos the left and right eye videos are stacked over/under and combined into one file resulting in half the resolution. If you don’t have the budget for stereo, don’t be too bummed as you can get more detail over stereo with 4-8k resolution out of your mono videos!

SPHERICAL vs CYLINDRICAL
If you have decided to stay mono, there are quite a range of options for you to choose from that offer high resolution. Again, pick the rig based on the style and type of content you are shooting. If you are shooting landscape with minimal subjects, then a cylindrical rig with more cameras around will offer extra high resolution. There will be more camera coverage around the horizon. However, because of the limited vertical fov, there will be nadir or zenith hole which may be ok because the viewer will not be looking at the sky or floor most of the time. If you are shooting for a fulldome, the nadir hole won’t be a problem. The sky and floor can also be shot with an extra camera so you can capture the information and patch in the nadir hole or replace the tripod in post. A cylindrical rig is not ideal if you have multiple subjects moving around between cameras. More money, more problems. More cameras, more seams!

A spherical hemicube rig is an option if you have a smaller budget and less cameras on hand. There will be equal coverage between the cameras including the zenith and nadir. 

FISHEYE vs WIDE-ANGLE
Another option for rigs is to modify the camera with fisheye lens. You can achieve a greater fov than wide angle lens and have more coverage per camera. Then you will need less cameras for the rig, which allows the cameras to be closer together and have less parallax. An advantage of this rig is allowing subjects to get up close to the camera because there are less cameras and seam lines to break. 

RECOMMENDED MODELS
MONO 
\begin{itemize}
\item 6 hemicube camera rig
\item 10 camera rig
\item 3 camera modified fisheye rig
\item 4 camera modified fisheye rig 

\end{itemize}

STEREO 
\begin{itemize}
\item 12 camera rig
\item 14 camera rig
\item 6 camera modified fisheye rig
\item 8 camera modified fisheye rig


\end{itemize}
            
MODELS OF THE UNIVERSE
ILLUSTRATION HERE
                
Find the balance between the FACTORS
TIME...is money
MONEY...is power
DISTANCE...is time apart 
DEPTH...is love
CONTROL…is an illusion
RESOLUTION...is a state of mind


\clearpage\end{CJK*}

\clearpage
\end{fullwidth}
