\chapter{The Elements}
\pagecolor{white}
\label{chap:1}
\begin{fullwidth}

{\itshape\bfseries “Welcome, O life! I go to encounter for the millionth time the reality of experience and to forge in the smithy of my soul the uncreated conscience of my race.”}

- James Joyce, A Portrait of the Artist as a Young Man
\vspace{\baselineskip}

\problem

{\large You want to be the next first greatest VR storyteller of all time and space. \par}

You want to create audiovisual immersive experiences. You want to expand cinema, compassion, and consciousness. You want to explore change. You want to create new tools for self awareness. You want to help write a new cinematic language. You want to break open that window of limited views and dive right into pure experience. You want to bring the world one step closer to putting ourselves in each other’s shoes. Hello, astronaut! That’s great what are the first steps to take you closer? What materials do you need to shoot, learn, and grow right here right now today?

\solution

{\large Dive deep in. No fear. Take the first step. Then the one after that. Gather all the elements and start experimenting! \par}

Here’s a basic checklist for your journey

\begin{itemize}
\item cameras
\item camera rig
\item tripod
\item audio slate/ring flash
\item micro SD cards
\item batteries
\item usb hub charger
\item hard drives
\item extra accessories: batteries, micro SD cards, cameras
\item courageous heart
\item your charming smile
\end{itemize}
                
have fun!

\begin{CJK*}{UTF8}{gbsn}
千里之行, 始於足下
\clearpage\end{CJK*}

\clearpage
\end{fullwidth}
